### 2014-02-26 paper/concrete.tex
Fix typo and put in the proof.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    Consider a language \tar{L} with configurations |tc|, reduction
    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
    language \ifc{L} with configurations |ic|, reduction relation
    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
    = id$, $f^{-1} \circ f^{-1} = id$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
    Then if \ifc{L} satisfies termination sensitive non-interference,
    then \tar{L} satisfies termination sensitive non-interference.
\end{theorem}

\begin{proof}
    Easy application of TSNI \tar{L} by applying $f$
\end{proof}

>>>>

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    Consider a language \tar{L} with configurations |tc|, reduction
    relation \tar{|.->|} and erasure function \tar{|erasef l|} and a
    language \ifc{L} with configurations |ic|, reduction relation
    \ifc{|.->|} and erasure function \ifc{|erasef l|}.  We say that
    \tar{L} and \ifc{L} are isomorphic if there exist (total) functions
    $f : |tc -> ic|$ and $f^{-1} : |ic -> tc|$ such that $f \circ f^{-1}
    = id$, $f^{-1} \circ f = id$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
    Then if \ifc{L} satisfies termination sensitive non-interference,
    then \tar{L} satisfies termination sensitive non-interference.
\end{theorem}

\begin{proof}
    Easily shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
    configuration and derivation back.
\end{proof}
